---
title: "COVID-19 burden and vaccination — Austin, Texas"
author: "UT-Austin COVID-19 Modeling Consortium"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: hpstr
    highlight: github
---

<style type="text/css">
.main-container {
  max-width: 2400px;
  margin-left: auto;
  margin-right: auto;
}
</style>



```{r include=FALSE,fig.width=6, fig.height=6, fig.align='center',message=F}
library(tidyverse)
library(lubridate)
library(readxl)
library(cowplot)
library(tidycensus)
## census_api_key("3deb7c3e77d1747cf53071c077e276d05aa31407", install = TRUE, overwrite = TRUE)
library(sf)
library(ggiraph)

theme_set(theme_minimal_grid())

# load("Rout/2021-06-03-map_data.Rdata")
load("Rout/2021-06-21-map_data.Rdata")
# load("Rout/2021-05-28-map_data.Rdata")
# load("Rout/2021-05-04-map_data.Rdata")
"#b35806"
mycols1 <- c("#8c510a", "#01665e", "#f5f5f5")
mycols1 <- c("#01665e", "#8c510a", "#f5f5f5")
mycols1 <- c("#01665e", "#b35806", "#f5f5f5")

mycols_svi <- c("#542788", "#b35806", "#f7f7f7")
mycols1 <- mycols_svi

mycols2 <- c("#c51b7d", "#4d9221", "#f7f7f7")
mycols3 <- c("#b2182b", "#2166ac", "#f7f7f7")
mycols4 <- c("#d73027", "#4575b4", "#ffffbf")
mycols5 <- c("#b2182b", "#4d4d4d", "#ffffff")
mycols6 <- c("#b35806", "#542788", "#f7f7f7")
mycols_death <- c("#762a83", "#1b7837", "#f7f7f7")
mycols_death <- c("#762a83", "#4b6116", "#f7f7f7")

mycols_death <- c("#b2182b", "#4d4d4d", "#f7f7f7")
mycols_death <- c("#610e17", "#4d4d4d", "#f7f7f7")

label_183 <- function(x) annotate(geom="text", x=-97.8, y=30.55, label="US 183", size=4)
label_I35 <- function(x)   annotate(geom="text", x=-97.68, y=30.55, label="I-35", size=4)
```



```{r include=FALSE, echo=FALSE}

# ZIP code: 
# Vaccine coverage: XX.X%
# Infection rate: 
# SVI: 
# Mortality rate: XX per 10,000

vax_sub_deaths <- vax_sub_deaths %>% 
  mutate(ZCTA_label = 
           sprintf("ZIP code: %s\nInfection rate: %2.1f%%\nMortality rate: %2.1f per 10,000 residents\nVaccine coverage: %2.1f%%\nSVI: %1.2f", 
                   ZCTA, 
                   round(attack_rate_mean * 100, 1),
                   round(deaths_per_10k, 2),
                   round(coverage * 100, 1),
                   round(SVI, 2)))

vax_sub_deaths <- vax_sub_deaths %>% 
  mutate(ZCTA_label = ZCTA,
         ZCTA_label_burden = 
           sprintf("ZIP: %s\nInfection rate: %2.1f%%", 
                   ZCTA, 
                   round(attack_rate_mean * 100, 1)
                   ),
         ZCTA_label_coverage = 
           sprintf("ZIP: %s\nVaccine coverage: %2.1f%%", 
                   ZCTA, 
                   round(coverage_total_pop * 100, 1)
                   ),
         ZCTA_label_SVI = 
           sprintf("ZIP: %s\nSVI: %1.3f", 
                   ZCTA, 
                   round(SVI, 3)
                   ),
         ZCTA_label_mortality = 
           sprintf("ZIP: %s\nMortality rate per 100,000: %2.1f", 
                   ZCTA, 
                   round(deaths_per_100k, 1)
                   ),
         ZCTA_label_mortality_coverage_SVI = 
           sprintf("%s\nInfection rate: %2.1f%%\nMortality rate: %2.1f per 100,000\nVaccine coverage: %2.1f%%\nSVI: %1.3f",
                   ZCTA, round(attack_rate_mean * 100, 1),
                   round(deaths_per_100k, 1),
                   round(coverage_total_pop * 100, 1), round(SVI, 3)
                   ),
         ZCTA_label_mortality_coverage_SVI = 
           sprintf("%s\n4-week hosp. admits: %2.1f per 100,000\nMortality rate: %2.1f per 100,000\nVaccine coverage: %2.1f%%\nSVI: %1.3f",
                   ZCTA, round(admits_per_100k, 1),
                   round(deaths_per_100k, 1),
                   round(coverage_total_pop * 100, 1), round(SVI, 3)
                   )
           # sprintf("ZIP code: %s\nSVI: %1.2f", 
                   # ZCTA, 
                   # round(attack_rate_mean * 100, 1),
                   # round(deaths_per_10k, 2),
                   # round(coverage * 100, 1),
                   # round(SVI, 2))
)

vax_sub_deaths$ZCTA_label_coverage <- vax_sub_deaths$ZCTA_label_burden <- vax_sub_deaths$ZCTA_label_SVI <- vax_sub_deaths$ZCTA_label_mortality <- vax_sub_deaths$ZCTA_label_mortality_coverage_SVI

```

```{r include=FALSE, echo=FALSE}

midpoint_vax <- round(city_avg$coverage_all/0.05)*0.05

## Vaccination rate (adults)
map_vaccines <- vax_sub_deaths %>%
  mutate(coverage = pmin(1, coverage),
         coverage_total_pop = pmin(1, coverage_total_pop)) %>%
  ggplot() +
  ##
  geom_sf_interactive(aes(
    fill=coverage_total_pop,
    ## fill=coverage,
    label=ZCTA,
    geometry=geometry,
    tooltip = ZCTA_label_coverage,
    data_id = ZCTA_label
  ), size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  ## Color scale
  scale_fill_steps2(
    "",
    ## midpoint=round(city_avg$coverage/0.1)*0.1,
    # midpoint=round(city_avg$coverage_all/0.05)*0.05,
    midpoint=midpoint_vax,
    high = mycols3[2], low = mycols3[1], mid = mycols3[3],
    breaks=sort(c(seq(0, 1, by=0.15), midpoint_vax)),
# scales::breaks_width(0.1),
    ## breaks=seq(0, 0.9, by=0.1),
    labels=scales::label_percent(accuracy=1),
    ) +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 17, barheight = 0.5)) +
  ## Labs
  labs(title="SARS-CoV-2 vaccine coverage\n(at least one dose)")+
  # labs(title="Vaccine coverage")  +
  theme_map() +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"))

## SVI
map_svi <- vax_sub_deaths %>%
  mutate(coverage = ifelse(coverage > 1, 1, coverage)) %>%
  ggplot() +
  geom_sf_interactive(
    aes(fill=SVI,
        label=ZCTA,
        geometry=geometry,
        tooltip = ZCTA_label_SVI,
        data_id = ZCTA_label),
    size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  scale_fill_steps2(
    "",
    midpoint=round(city_avg$SVI/0.05)*0.05,
    high = mycols1[1], low = mycols1[2], mid = mycols1[3],
    breaks=seq(0, 0.9, by=0.1)
  ) +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 15, barheight = 0.5)) +
  NULL +
  labs(title="Social vulnerability")  +
  theme_map() +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"))

## Plot of admits
map_admits <- vax_sub_deaths %>%
  mutate(
    admits_per_100k = ifelse(admits_per_100k > 35, NA, admits_per_100k)
  ) %>% 
  # mutate(admits_per_100k = case_when(
    # admits_per_100k > 40 ~ NA,
    # TRUE ~ admits_per_100k
  # )) %>%
  # filter(admits_per_100k != max(admits_per_100k)) %>%
  # filter(admits_per_100k != max(admits_per_100k)) %>%
  ggplot() +
  geom_sf_interactive(
    aes(fill=admits_per_100k,
        label=attack_rate_mean,
        geometry=geometry,
        tooltip = ZCTA_label_burden,
        data_id = ZCTA_label),
    size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  scale_fill_steps2(
    "",
    midpoint=round(city_avg$admits_per_100k_avg/5)*5,
    high = mycols2[1], low = mycols2[2], mid = mycols2[3],
    breaks=seq(5, 50, by=5),
    # breaks=seq(0.1, 0.9, by=0.1),
    # labels=scales::label_percent(accuracy=1),
    ) +
  NULL +
  labs(title="COVID-19 hospital admissions per 100,000\n(past four weeks)") + 
  # labs(title="Four-week hospital admissions per 100,000")  +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 15, barheight = 0.5)) +
  theme_map() +
  annotate(geom="text", x=-97.8, y=30.55, label="US 183", size=4)+
  annotate(geom="text", x=-97.68, y=30.55, label="I-35", size=4) +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"))

## Plot of cumulative infections
map_burden <- vax_sub_deaths %>%
  ggplot() +
  geom_sf_interactive(
    aes(fill=attack_rate_mean,
        label=attack_rate_mean,
        geometry=geometry,
        tooltip = ZCTA_label_burden,
        data_id = ZCTA_label),
    size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  scale_fill_steps2(
    "",
    midpoint=round(city_avg$infection_rate/0.1)*0.1,
    high = mycols2[1], low = mycols2[2], mid = mycols2[3],
    breaks=seq(0.1, 0.9, by=0.1),
    labels=scales::label_percent(accuracy=1),
    ) +
  NULL +
  labs(title="Cumulative infections")  +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 15, barheight = 0.5)) +
  theme_map() +
  annotate(geom="text", x=-97.8, y=30.55, label="US 183", size=4)+
  annotate(geom="text", x=-97.68, y=30.55, label="I-35", size=4) +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"))

## Mortality rate
map_mortality <- vax_sub_deaths %>%
  # glimpse() %>%
  ggplot() +
  geom_sf_interactive(
    aes(fill=deaths_per_100k,
        label=ZCTA,
        geometry=geometry,
        tooltip = ZCTA_label_mortality,
        data_id = ZCTA_label
              ), size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  scale_fill_steps2(
    "",
    midpoint=round(city_avg$deaths_per_100k_avg/5)*5,
    high = mycols_death[1],
    low = mycols_death[2],
    mid = mycols_death[3],
    breaks=seq(25, 150, by=25)
  ) +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 14, barheight = 0.5)) +
  labs(title="In-hospital COVID-19 deaths per 100,000")  +
  # theme_map() +
  theme_map() +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"))

io <- vax_sub_deaths %>%
  ## filter(state == "Texas") %>%
  select(date,
         ZCTA,
         PO_NAME,
         county = COUNTY,
         county_fips,
         tsa,
         msa,
         state,
         total_pop = B01001_001E,
         adult_pop,
         adult_pop_65plus = plus65,
         senior_frac,
         under16_pop = under16,
         doses_administered,
         one_dose,
         fully_vaccinated,
         coverage_one_dose_16plus = coverage,
         coverage_one_dose_total_pop = coverage_total_pop,
         dem_share,
         ## dem_share_2party_pres_vote,
         ## state_average_coverage_one_dose = state_average,
         # contains("phase"),
         median_household_income = median_incomeE,
         SVI,
         contains("RPL"),
         admits_4week = admits_imp, 
         deaths,
         admits_4week_per_100k = admits_per_100k,
         deaths_per_100k,
         geometry) %>% 
  as.data.frame() %>%
  select(-date, -geometry) %>% 
  glimpse() %>%
  write_csv("austin_vaccinations_svi.csv")

```




```{r fig.width=12, fig.height=11, fig.align='center', echo=FALSE, message=FALSE}

mygrid_all <- plot_grid(
  map_burden, map_mortality,
  map_svi, map_vaccines,
  nrow=2)

mygrid_all <- plot_grid(
  map_admits, map_mortality,
  map_svi, map_vaccines,
  nrow=2)


tooltip_css <- "background-color:#424242;color:white;padding:10px;border-radius:5px;opacity:0.1;"
#8a8a8a

tooltip_css <- "background:rgba(0,0,0,.5);color:white;padding:10px;border-radius:5px;opacity:0.01;"

girafe(
  ggobj = mygrid_all,
  width_svg = 12,
  height_svg = 11,
    options = 
  list(
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.2;"),
    opts_hover(css = "stroke:black;stroke-width:1.2;")
  )
  )


```



## COVID-19 mortality, vaccination, and vulnerability for each ZIP code

```{r fig.width=4, fig.height=4, fig.align='center', echo=FALSE, message=FALSE,warning=F}

myscatter_final <- vax_sub_deaths %>%
  filter(coverage <= 1 & coverage_total_pop >=0.2) %>% 
  ## mutate(coverage = ifelse(coverage > 1, 1, coverage)) %>% 
  ggplot() +
  geom_smooth(aes(deaths_per_100k, coverage_total_pop),method="lm") +
  geom_point_interactive(aes(deaths_per_100k, coverage_total_pop,
                            tooltip = ZCTA_label_mortality_coverage_SVI,
        data_id = ZCTA_label, 
                 col = SVI## , col=B01002_001E
                 ## , col = burden
                 ),
             size = 2.5## , alpha=0.5
             ) +
  ## scale_color_distiller(palette = "Spectral") +
  scale_color_steps2(
    "Social vulnerability",
    midpoint=round(city_avg$SVI/0.05)*0.05,
    high = mycols1[1], low = mycols1[2], mid = mycols1[3],
    breaks=seq(0, 0.9, by=0.1)
  ) + 
  # scale_color_viridis_c("Social vulnerability",
                        # option="C") +
  scale_y_continuous(labels=scales::percent) +
  # scale_x_continuous(labels=scales::percent) + 
  labs(## title = "Cumulative infections, vaccine coverage, & social vulnerability in Austin", 
    # subtitle = "Percentage of total population receiving at least one dose",
       y = "Vaccine coverage",
       x = "In-hospital COVID-19 deaths per 100,000") +
  guides(color = guide_colorsteps(ticks=TRUE,barwidth = 12, barheight = 0.5)) +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "grey"),
        legend.key = element_rect(fill = "grey", color = NA),
        ## legend.box.background = element_rect(fill = "lightgrey"),
        panel.grid.major = element_line(colour = "grey90"))

map_svi2 <- vax_sub_deaths %>%
  mutate(coverage = ifelse(coverage > 1, 1, coverage)) %>%
  ggplot() +
  geom_sf_interactive(
    aes(fill=SVI,
        label=ZCTA,
        geometry=geometry,
        tooltip = ZCTA_label_SVI,
        data_id = ZCTA_label),
    size=0.1) +
  ## Roads
  geom_sf(data = atx_roads,
          col = "grey10") +
  # label_183() + label_I35() +
  scale_fill_steps2(
    # "Social vulnerability",
    midpoint=round(city_avg$SVI/0.05)*0.05,
    high = mycols1[1], low = mycols1[2], mid = mycols1[3],
    breaks=seq(0, 0.9, by=0.1)
  ) + 
  # scale_fill_viridis_c("Social vulnerability",
                        # option="C") +
  guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 15, barheight = 0.5)) +
  NULL +
  labs(title="Social Vulnerability"
       # subtitle=""
       )  +
  theme_map() +
  theme(legend.position = "none",
        legend.title = element_text(face = "bold"))

scatter_grid <- plot_grid(myscatter_final, map_svi2, nrow=1, rel_widths = c(2,1))
scatter_grid <- plot_grid(map_svi2, myscatter_final, nrow=1, rel_widths = c(1,2))

scatter_grid <- plot_grid(myscatter_final, nrow=1, rel_widths = c(1,2))

girafe(
  ggobj = scatter_grid,
  width_svg = 7,
  height_svg = 5,
    options =
  list(
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.2;"),
    opts_hover(css = "stroke:black;stroke-width:1.2;")
  )
)

## girafe(
##   ggobj = myscatter_final,
##   width_svg = 7,
##   height_svg = 5,
##     options = 
##   list(
##     opts_tooltip(css = tooltip_css),
##     opts_hover_inv(css = "opacity:0.2;"),
##     opts_hover(css = "stroke:black;stroke-width:1.2;")
##   )
## )

```

## Average vaccine coverage by SVI quartile

```{r fig.width=4, fig.height=4, fig.align='center', echo=FALSE, message=FALSE,warning=F}
# load("Rout/2021-05-05-vax-time.Rdata")


mypo <- "Austin"

if (ls() %>% str_detect("myvax_all") %>% any()) {
  vax_all <- myvax_all
}

vax_time <- vax_all %>%
  filter(one_dose_new > 0) %>%
  filter(PO_NAME == mypo) %>%
  left_join(mysvimap %>% select(ZCTA, SVI_cat = quantile_cat), alpha=0.1) %>%
  ggplot() +
  ## geom_line(aes(date, coverage, group=ZCTA, col = SVI_cat),lty="dashed") +
  geom_line_interactive(data = mydf,
            aes(date, coverage_cat, col = SVI_cat,
                data_id=SVI_cat,
        tooltip = SVI_cat), 
        size = 1.1) +
  geom_point_interactive(data = mydf,
             aes(date, coverage_cat, col = SVI_cat,
                 data_id=SVI_cat,
        tooltip = SVI_cat), 
        size = 3) +
  scale_y_continuous(labels=scales::label_percent(accuracy=1), breaks = seq(0, 1.5,by=0.2)) +
  labs(
    # x`title = sprintf("Average vaccine coverage by SVI quartile", mypo),
       # subtitle = "% of 16+ population with at least one dose",
       x = "Date (2021)", y = "Vaccine coverage") +
  scale_color_brewer("SVI quartile\n(higher is more vulnerable)",
                     palette="Blues")+
  theme_minimal_grid(font_size=11)+
  ## scale_color_brewer("SVI quartile",
  ##                  palette="Dark2")+
  theme(panel.background = element_rect(fill = "darkgrey"),
        legend.key = element_rect(fill = "darkgrey", color = NA),
        ## legend.box.background = element_rect(fill = "lightgrey"),
        panel.grid.major = element_line(colour = "grey90"),
        legend.position="bottom")

# vax_time




vax_time2 <- vax_all %>%
  filter(one_dose_new > 0) %>%
  filter(PO_NAME == mypo) %>%
  arrange(desc(date)) %>%
  left_join(mysvimap %>% select(ZCTA, SVI_cat = quantile_cat)) %>%
  ggplot() +
  ## geom_line(aes(date, coverage, col = SVI_cat, group = ZCTA), alpha=0.2) +
  ## geom_smooth(aes(date, coverage, col = SVI_cat)) +
  ## geom_line(data = mydf,
  ##           aes(date, coverage_cat, col = SVI_cat, lty="Quartile average"), size = 1.5) +
  geom_line_interactive(data = mydf,
            aes(date, coverage_sincefeb_cat, col = SVI_cat,
                data_id=SVI_cat,
        tooltip = SVI_cat), 
        size = 1.1) +
  geom_point_interactive(data = mydf,
            aes(date, coverage_sincefeb_cat, col = SVI_cat,
                data_id=SVI_cat,
        tooltip = SVI_cat), size = 3) +
  scale_y_continuous(labels=scales::label_percent(accuracy=1), breaks = seq(0, 1.5,by=0.2)) +
  ## labs(title = "Average vaccine coverage in Austin ZIP codes by SVI quartile",
         labs(title = sprintf("Increase since Jan 31, 2021", mypo),
       # subtitle = "Increase in vaccine coverage since Jan 31, 2021",
       x = "Date (2021)", y = "Increase in vaccine coverage") +
  scale_color_brewer("SVI quartile\n(higher is more vulnerable)",
                     palette="Blues")+
  theme_minimal_grid(font_size=11)+
    ## scale_color_brewer("SVI quartile",
    ##                  palette="Dark2")+
    theme(panel.background = element_rect(fill = "darkgrey"),
        legend.key = element_rect(fill = "darkgrey", color = NA),
        ## legend.box.background = element_rect(fill = "lightgrey"),
        panel.grid.major = element_line(colour = "grey90"),
        legend.position="bottom") +
    ## scale_color_brewer("SVI quartile",
    ##                  palette="Dark2")+ 
  ## scale_color_viridis_c() +
  NULL

# vax_time2

# vax_sub_deaths 


vax_map <- vax_sub_deaths %>%
  left_join(mysvimap %>% select(ZCTA, SVI_cat = quantile_cat)) %>% 
  ## filter(coverage < 3) %>%
  mutate(coverage = ifelse(coverage > 1, 1, coverage)) %>% 
  ggplot() +
  geom_sf_interactive(
    aes(fill=SVI_cat, label=ZCTA, geometry = geometry,
              data_id=SVI_cat,
        tooltip = SVI_cat
              ## , col=burden
              ), size=0.1) +
  geom_sf(data = atx_roads,
          col = "grey10") +
  label_183() + label_I35() +
  ## scale_fill_brewer(palette="Dark2") +
  # scale_fill_brewer("SVI\nquartile\n(higher is\nmore\nvulnerable)", palette="Blues") + 
  scale_fill_brewer("SVI\nquartile", palette="Blues") + 
  ## geom_sf(data = I35_2,
  ##         col = "grey10") +
  ## geom_sf(data = missing_183_2,
  ##         col = "grey10") +
  ## geom_sf(data = US183_2,
  ##         col = "grey10") +
  ## labs(title = "Map of Austin ZIP codes by SVI quartile") +
  ## labs(title = "Map of Houston ZIP codes by SVI quartile") +
  # labs(title = sprintf("Map of %s ZIP codes by SVI quartile", mypo)) +
  ## scale_fill_viridis_c("") + 
  ## scale_fill_gradient2(## sprintf("Vaccine coverage"),
  ##   "",
  ##   ## breaks=c(0.3, round(city_avg$coverage, 2), 0.5, 0.7, 0.9),
  ##                      midpoint=city_avg$coverage, labels=scales::label_percent(accuracy=1),
  ##                      high = mycols3[2], low = mycols3[1], mid = mycols3[3]
  ##                      ## , mid="grey90"
  ##                      ## , low="firebrick3",high = "dodgerblue3"
  ## ) +
  ## labs(title="Vaccine coverage")  +
  ## guides(fill = guide_coloursteps(ticks=TRUE,barwidth = 12, barheight = 0.5)) +
  theme_map(font_size = 11) +
  guides(fill = guide_legend(ncol = 1)) + 
  ## annotate(geom="text", x=-97.8, y=30.5, label="US 183", size=5)+
  ## annotate(geom="text", x=-97.68, y=30.5, label="I-35", size=5) + 
  theme(## legend.position = "bottom"## ,
        legend.position = "bottom"## ,
        ## legend.title = element_text(face = "bold")
        )

speed_grid <- plot_grid(plot_grid(vax_time + theme(legend.position = "none"), 
                                  vax_time2 + theme(legend.position="none"),
                                  nrow=2), vax_map, rel_widths = c(2, 1))


speed_grid <- plot_grid(plot_grid(vax_time + theme(legend.position = "none"), 
                                  # vax_time2 + theme(legend.position="none"),
                                  nrow=1), vax_map, rel_widths = c(2, 1))


girafe(
  ggobj = speed_grid,
  width_svg = 7,
  height_svg = 5,
    options =
  list(
    opts_tooltip(css = tooltip_css),
    opts_hover_inv(css = "opacity:0.2;"),
    opts_hover(css = "stroke:black;stroke-width:0.6;")
  )
)

```


<!-- ## Partial immunity to SARS-CoV-2 infection in Travis County by age group -->
<!-- ```{r fig.width=4, fig.height=4, fig.align='center', echo=FALSE, message=FALSE,warning=F} -->

<!-- mynamevec <- c("Prior infection", "Vaccination", "Combined immunity") -->

<!-- travis_inf_agegroup3_long <- -->
<!--   read_csv(sprintf("Rout/2021-05-05-immunity.csv", today())) %>%  -->
<!--   # read_csv(sprintf("Rout/%s-immunity.csv", today())) %>%  -->
<!--   mutate(name2 = factor(name2, levels = mynamevec)) -->

<!-- immunity_plot <- travis_inf_agegroup3_long %>% -->
<!--   ggplot() + -->
<!--   geom_col_interactive(aes( -->
<!--     age_group, value, fill = name2, -->
<!--     tooltip = age_group_level, data_id = age_group), col="grey", size=0.5, alpha=0.9) + -->
<!--   geom_text(aes(age_group, value+0.05, label=sprintf("%2.f%%", value * 100))) + -->
<!--   facet_wrap(~name2) + -->
<!--   theme_minimal_hgrid(font_size = 11) + -->
<!--   theme(axis.text.x = element_text(angle=45, vjust=0.5, hjust=0.5)) + -->
<!--   guides(fill = FALSE) + -->
<!--   scale_y_continuous(limits = c(0, 1.05), -->
<!--                      breaks=seq(0, 1, by=0.2), labels=scales::label_percent(accuracy=1)) + -->
<!--   scale_fill_manual(values=c("firebrick3", "dodgerblue3", "goldenrod")) + -->
<!--   labs( -->
<!--     # title = "Partial immunity to SARS-CoV-2 infection by age group", -->
<!--        subtitle = "\"Combined immunity\" assumes that vaccination and prior infection are independent", -->
<!--        x = "Age group", y = "Partial immunity percentage") -->

<!-- # immunity_plot -->

<!-- girafe( -->
<!--   ggobj = immunity_plot, -->
<!--   width_svg = 7, -->
<!--   height_svg = 5, -->
<!--     options = -->
<!--   list( -->
<!--     opts_tooltip(css = tooltip_css), -->
<!--     opts_hover_inv(css = "opacity:0.2;"), -->
<!--     opts_hover(css = "stroke:black;stroke-width:1.2;") -->
<!--   ) -->
<!-- ) -->

<!-- ``` -->


## Data sources

**COVID-19 hospital admissions** and **in-hospital COVID-19 mortality** are based on line list patient data provided by all area hospitals on a weekly basis.

<!-- We receive regular (at least weekly) updates on **hospitalization data**, both admissions and mortality, from the City of Austin which includes patient's ZIP code of residence.  -->

**Social vulnerability** estimates are based on the CDC’s social vulnerability index (SVI), which weighs local factors such as socioeconomic status, household composition, non-English language, and transportation access which "may affect that community’s ability to prevent human suffering and financial loss in the event of disaster."  A higher SVI value indicates that an area is more vulnerable.  See the [SVI documentation on the CDC's website][SVI].

<!-- For **social vulnerability**, we use the CDC's social vulnerability index ([SVI][SVI]), which weighs local factors such as socioeconomic status, household composition, non-English language, and transportation access which "may affect that community’s ability to prevent human suffering and financial loss in the event of disaster." -->

**SARS-CoV-2 vaccination coverage** estimates are based on ZIP code level vaccine administration data provided by the [Texas Department of State Health Services COVID-19 data website][DSHS]. For each ZIP code, we divide the reported ZIP code population size (based on the [2019 American Community Survey][ACS]) by the number of individuals who have received at least one dose of vaccine.

This page is current as of `r lubridate::today()`

<!-- We download **vaccine administration data by ZIP code** from the website of the [Texas Department of State Health Services][DSHS].  To calculate vaccine coverage, we divide the number of people in a ZIP code with at least one dose by the total ZIP code population.  We use the Census Bureau's [2019 American Community Survey][ACS] to access data for population by ZIP code. -->

## Credits

Spencer Woody, Emily Javan, Kaitlyn Johnson, Remy Pasco, Maureen Johnson-León, Michael Lachmann, Spencer J. Fox, and Lauren Ancel Meyers

[UT-Austin COVID-19 Modeling Consortium](https://covid-19.tacc.utexas.edu)

## Contact

[Spencer Woody](https://spencerwoody.github.io)  
Email to `spencer.woody [at] utexas [dot] edu`

Download the code and data [here][ghdata].

[ghdata]: https://github.com/spencerwoody/texvax/tree/main/
[SVI]: https://www.atsdr.cdc.gov/placeandhealth/svi/index.html
[DSHS]: https://www.dshs.texas.gov/coronavirus/additionaldata/
[ACS]: https://www.census.gov/programs-surveys/acs/
